Icicle: write once, run once

### 2016-05-28 2016fhpc/section/04-Benchmarks.tex
just mention size of larger datasets in benchs

We are currently using Icicle in production, over medium-sized datasets (around three hundred gigabytes) that fit on a single disk.
While future versions will require incremental computation, the runtime processing medium-sized datasets has been small enough to run over the entire dataset each time.
These initial results have been very promising, and we are currently implementing distribution across multiple machines for datasets that do not fit on a single disk.
Incremental computation becomes more important for this distributed case, as it can potentially avoid copying terabytes of data over the network.

>>>>

We are currently using Icicle in production, over medium-sized datasets (around three hundred gigabytes uncompressed) that fit on a single disk.
While future versions will require incremental computation, the runtime processing medium-sized datasets has been small enough to run over the entire dataset each time.
These initial results have been very promising, and we are currently implementing distribution across multiple machines to handle datasets that are tens of terabytes compressed, and do not fit on a single disk.
Incremental computation becomes more important for this distributed case, as it can potentially avoid copying terabytes of data over the network.
